---
title: "Tutorial: Quantifying Natural Selection"
output: html_notebook
---

```{r Preliminaries, message=FALSE, warning=FALSE, include=FALSE}
## LOAD REQUIRED LIBRARIES & SET OPTIONS ----
library(tidyverse)
library(cowplot) # pretty default ggplots
#library(broom) # for tidying multiple linear models

## LOAD & MANAGE DATASET ----

gall_selection.df <- read_csv("gall_selection_data.csv") %>%
  mutate(Plant_Position = as.character(Plant_Position),
         Gall_Number = as.character(Gall_Number),
         Treatment.focus = as.character(Treatment.focus),
         Treatment = as.character(Treatment),
         Genotype = as.character(Genotype),
         Gall_Letter = as.character(Gall_Letter)) %>%
  unite(Gall_ID, Gall_Number, Gall_Letter, remove = FALSE) %>%
  
  # subset data for analysis
  filter(phenology == "early", Location == "tree",
         platy > 0 | ectos > 0 | pupa > 0) %>%                  # eliminate unknown sources of mortality
  mutate(gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
         egg_parasitoid = as.numeric(ifelse(platy > 0, 1, 0))) 

# create a new dataset that compares phenotypic distributions before and after selection
galls_before <- mutate(gall_selection.df, Timing="Before")
galls_after <- filter(gall_selection.df, gall_survival == 1) %>% mutate(Timing = "After")

gall_diffs.df <- bind_rows(galls_before, galls_after)
```

Evolution by natural selection requires three basic ingredients: (1) variation in phenotypes; (2) variation in fitness; and (3) heritabile phenotypic variation. Although heritability is a key component to predicting evolutionary change, we can ignore it if we just focus on quantifying natural selection, which requires just the first two ingredients. 

Perhaps the easiest way to quantify natural selection is by calculating the *selection differential* ($s$), which corresponds to the change in mean phenotype ($z$) after selection: $$s=\bar{z}^*-\bar{z}$$. For my galling insects, this is straightforward to measure. I calculate the mean phenotype of all galls and compare it to the mean phenotype of surviving insects. Below is an example with gall size:

```{r figure: gall size selection differential, echo=FALSE, message=FALSE, warning=FALSE}
size_means_diffs <- gall_diffs.df %>%
  group_by(Timing, Treatment.focus) %>%
  summarise_at(vars(Gall_Height_mm, gall_survival), funs(mean, var, sd)) 

sd_size_before <- filter(size_means_diffs, Treatment.focus=="Control", Timing=="Before")$Gall_Height_mm_var

size_differentials <- size_means_diffs %>%
  select(Timing, Treatment.focus, Gall_Height_mm_mean) %>%
  spread(Timing, Gall_Height_mm_mean) %>%
  mutate(selection_differential = After - Before)

s_size <- filter(size_differentials, Treatment.focus=="Control")$selection_differential
sc_s_size <- s_size/sd_size_before

gall_diffs.df %>%
  filter(Treatment.focus == "Control") %>%
  ggplot(., aes(x=Gall_Height_mm, fill=Timing)) +
  geom_density(alpha=0.5) +
  geom_vline(data=filter(size_means_diffs, Treatment.focus=="Control"), aes(xintercept=Gall_Height_mm_mean, color=Timing), linetype="dashed") #+
  #facet_wrap(~Treatment.focus, ncol = 1)
```



Here, the $s=0.83$. Note that this selection differential is unstandardized. This makes it difficult to compare the strength of selection acting on different phenotypes both within and across studies. We can calculate the standardized selection differential as: $$S'=\frac{S}{\sigma_z}$$

For gall size, $S'=0.18$.

There is another way that we can express and visualize selection differentials, name as the covariance between phenotype and relative fitness: $$S=cov(w,z)$$

where relative fitness is calculated as absolute fitness ($W$) divided by the mean fitness of the population: $$w=\frac{W}{\bar{W}}$$

Let's visualize what this looks like with the gall data:

```{r}
W_bar_control <- filter(size_means_diffs, Treatment.focus=="Control", Timing=="Before")$gall_survival_mean
control_df <- gall_selection.df %>%
  filter(Treatment.focus=="Control") %>%
  mutate(relative_fitness = gall_survival/W_bar_control)

with(control_df, cov(relative_fitness, Gall_Height_mm))

summary(lm(relative_fitness ~ I(Gall_Height_mm - mean(Gall_Height_mm)), control_df))

0.83/sd(control_df$Gall_Height_mm) # standardized selection differential
0.83/var(control_df$Gall_Height_mm) # selection gradient

ggplot(control_df, aes(x=Gall_Height_mm, y=relative_fitness)) +
  geom_jitter(height=0.1, shape=1) +
  geom_smooth(method="lm") +
  geom_hline(yintercept=1, linetype="dotted", color="grey") +
  geom_vline(xintercept=filter(size_means_diffs, Treatment.focus=="Control", Timing=="Before")$Gall_Height_mm_mean, 
             linetype="dotted", color="grey")
```

This gives us the same estimate of selection differential as before.


## Calculating selection in different environments

```{r}

# (1) calculate relative fitness for each environment separately
W_bar_treatment <- filter(size_means_diffs, Treatment.focus=="Ectoparasitoid exclusion", Timing=="Before")$gall_survival_mean; W_bar_treatment

gall_selection.df <- gall_selection.df %>%
  mutate(relative_fitness = ifelse(Treatment.focus=="Control", gall_survival/W_bar_control, gall_survival/W_bar_treatment))

ggplot(gall_selection.df, aes(x=Gall_Height_mm, y=relative_fitness, color=Treatment.focus)) +
  geom_jitter(height=0.1, shape=1) +
  geom_smooth(method="lm") +
  geom_hline(yintercept=1, linetype="dotted", color="grey") +
  geom_vline(data = filter(size_means_diffs, Timing=="Before"), aes(xintercept=Gall_Height_mm_mean, color=Treatment.focus), linetype="dotted")
```

Let's dissect this a bit further...

```{r}
ggplot(gall_selection.df, aes(x=Gall_Height_mm, y=gall_survival, color=Treatment.focus)) +
  geom_jitter(height=0.05, shape=1) +
  geom_smooth(method="lm") +
  #geom_hline(yintercept=1, linetype="dotted", color="grey") +
  geom_vline(data = filter(size_means_diffs, Timing=="Before"), aes(xintercept=Gall_Height_mm_mean, color=Treatment.focus), linetype="dotted") +
  scale_y_continuous(breaks=c(0,0.25,0.5,0.75,1))

summary(lm(gall_survival ~ Treatment.focus*I(Gall_Height_mm - mean(Gall_Height_mm)), gall_selection.df))
```

Interesting. So there doesn't appear to be a difference in the relationship between gall survival and gall size between treatments. Therefore, the differences in selection gradients between treatments is due to differences in relative fitness between environments. 

So where do I go from here? In my view, the differences in relative fitness are an experimental artifact of the reduction in parasitoid diversity, and therefore, there hasn't been a chance for the parasitoid in the simple community to compensate in terms of its abundance over multiple generations and make up for the differences in relative fitness.

Some exploratory analyses:

```{r}
with(control_df, cov(relative_fitness, Gall_Height_mm))

summary(lm(relative_fitness ~ I(Gall_Height_mm - mean(Gall_Height_mm)), control_df))

with(control_df, cov(relative_fitness, gall_individuals))

# adding gall individuals
summary(lm(relative_fitness ~ 
             I(Gall_Height_mm - mean(Gall_Height_mm)) + 
             I(gall_individuals - mean(gall_individuals)), 
           control_df))

# adding gall density
summary(lm(relative_fitness ~ 
             I(Gall_Height_mm - mean(Gall_Height_mm)) + 
             I(gall_individuals - mean(gall_individuals)) +
             I(Density_per_100_shoots - mean(Density_per_100_shoots)),
           control_df))

## treatment focus
summary(lm(relative_fitness ~ I(Gall_Height_mm - mean(Gall_Height_mm)), 
           filter(gall_selection.df, Treatment.focus=="Ectoparasitoid exclusion")))

summary(lm(relative_fitness ~ 
             I(Gall_Height_mm - mean(Gall_Height_mm)) + 
             I(gall_individuals - mean(gall_individuals)), 
           filter(gall_selection.df, Treatment.focus=="Ectoparasitoid exclusion")))

summary(lm(relative_fitness ~ 
             I(Gall_Height_mm - mean(Gall_Height_mm)) + 
             I(gall_individuals - mean(gall_individuals)) +
             I(Density_per_100_shoots - mean(Density_per_100_shoots)),
           filter(gall_selection.df, Treatment.focus=="Ectoparasitoid exclusion")))

## with treatment variable
summary(lm(relative_fitness_adj ~ 
             I(Gall_Height_mm - mean(Gall_Height_mm)) + Treatment.focus:I(Gall_Height_mm - mean(Gall_Height_mm)) +
             I(gall_individuals - mean(gall_individuals)) + Treatment.focus:I(gall_individuals - mean(gall_individuals)) +
             I(Density_per_100_shoots - mean(Density_per_100_shoots)) + Treatment.focus:I(Density_per_100_shoots - mean(Density_per_100_shoots)),
           gall_selection.df))

W_bar_platy_control <- mean(filter(gall_selection.df, Treatment.focus=="Control")$egg_parasitoid)
W_bar_platy_treatment <- mean(filter(gall_selection.df, Treatment.focus=="Ectoparasitoid exclusion")$egg_parasitoid)

W_bar_treatment_adj <- W_bar_treatment - (W_bar_platy_treatment - W_bar_platy_control); W_bar_treatment_adj

gall_selection.df <- gall_selection.df %>%
  mutate(relative_fitness_adj = ifelse(Treatment.focus=="Control", gall_survival/W_bar_control, gall_survival/W_bar_treatment_adj))

summary(lm(relative_fitness_adj ~ 
             scale(Gall_Height_mm) + Treatment.focus:scale(Gall_Height_mm) +
             scale(gall_individuals) + Treatment.focus:scale(gall_individuals) +
             scale(Density_per_100_shoots) + Treatment.focus:scale(Density_per_100_shoots),
           gall_selection.df))

summary(lm(relative_fitness ~ 
             scale(Gall_Height_mm) + Treatment.focus:scale(Gall_Height_mm) +
             scale(gall_individuals) + Treatment.focus:scale(gall_individuals) +
             scale(Density_per_100_shoots) + Treatment.focus:scale(Density_per_100_shoots),
           gall_selection.df))
```

GSG package
```{r}
library(gsg)
library(mgcv)
library(visreg)

# experimenting with boot.case gave bootstrapped distributions that weren't centered near the model mean estimate.
# also, using 'refit.smooth = T' also generated some very skewed distributions
# the recipe below provided the most sensible estimates for my data
gradient.calc <- function(mod, phenotype, covariates = NULL) {
  gam.gradients(mod, phenotype, covariates, #parallel = 'multicore', ncpus = 32, 
                refit.smooth = F, 
                se.method = 'boot.para',
                standardized = T)
} 

gam.size.control <- gam(gall_survival ~ s(Gall_Height_mm), data = filter(gall_selection.df, Treatment.focus=="Control"))
summary(gam.size.control)
visreg(gam.size.control)

gradient.calc(gam.size.control, phenotype = "Gall_Height_mm")$ests

gam.size.treatment <- gam(gall_survival ~ s(Gall_Height_mm) + s(gall_individuals, k=9) + s(Density_per_100_shoots), data = filter(gall_selection.df, Treatment.focus=="Ectoparasitoid exclusion"))
summary(gam.size.treatment)
visreg(gam.size.treatment)

gradient.calc(gam.size.treatment, phenotype = "Gall_Height_mm", covariates = c("gall_individuals","Density_per_100_shoots"))$ests

```



Does the theory require multivariate normal phenotypes?

Examine distributions of phenotypes
```{r}
size_means <- gall_selection.df %>%
  group_by(Treatment.focus) %>%
  summarise_at(vars(Gall_Height_mm, gall_survival), funs(mean))
size_means

gall_selection.df %>%
  ggplot(., aes(x=Gall_Height_mm, fill=Treatment.focus)) +
  geom_density(alpha=0.5) +
  geom_vline(data=size_means, aes(xintercept=Gall_Height_mm, color=Treatment.focus), linetype="dotted")

# according to Shapiro-Wilk though, its non-normal (P < 0.05). 
# other transformations don't help, I think the raw distribution looks pretty good though
shapiro.test(gall_selection.df$Gall_Height_mm)
shapiro.test(sqrt(gall_selection.df$Gall_Height_mm))
shapiro.test(log(gall_selection.df$Gall_Height_mm))

## AGGREGATE DATA AT GALL LEVEL ----
# for analyzing the number of individuals per gall

agg_gall.level <- gall_selection.df %>%
  group_by(Treatment.focus, Genotype, Plant_Position, Gall_Number) %>%
  summarise_at(vars(gall_survival, gall_individuals, Gall_Height_mm, Density_per_100_shoots), funs(mean)) %>%
  mutate(log.gall_individuals = log(gall_individuals))

# I added a log-transformed 'gall individuals' because it helps normalize the distribution a bit
shapiro.test(agg_gall.level$gall_individuals)
shapiro.test(sqrt(agg_gall.level$gall_individuals))
shapiro.test(log(agg_gall.level$gall_individuals))

# calculate average number of individuals per gall in each treatment
indiv_means <- agg_gall.level %>%
  group_by(Treatment.focus) %>%
  summarise_at(vars(gall_individuals, log.gall_individuals, gall_survival), funs(mean))
indiv_means

agg_gall.level %>%
  ggplot(., aes(x=gall_individuals, fill=Treatment.focus)) +
  geom_histogram(position='identity', alpha=0.5, binwidth=1) +
  geom_vline(data=indiv_means, aes(xintercept=gall_individuals, color=Treatment.focus), linetype="dotted") +
  scale_x_continuous(breaks=c(1:10))

agg_gall.level %>%
  ggplot(., aes(x=log.gall_individuals, fill=Treatment.focus)) +
  geom_histogram(position='identity', alpha=0.5) +
  geom_vline(data=indiv_means, aes(xintercept=log.gall_individuals, color=Treatment.focus), linetype="dotted")


## AGGREGATE DATA AT TREE LEVEL ----
# for gall density analysis

agg_tree.level <- gall_selection.df %>%
  group_by(Treatment.focus, Genotype, Plant_Position) %>%
  summarise_at(vars(gall_survival, gall_individuals, Gall_Height_mm, Density_per_100_shoots), funs(mean)) %>%
  mutate(sqrt.Density_per_100_shoots = sqrt(Density_per_100_shoots))

# I added a square-root transformation to gall density because it makes the distribution more normal (but not quite)
shapiro.test(agg_tree.level$Density_per_100_shoots)
shapiro.test(sqrt(agg_tree.level$Density_per_100_shoots))
shapiro.test(log(agg_tree.level$Density_per_100_shoots+1))

# calculate the average gall density in each treatment
density_means <- agg_tree.level %>%
  group_by(Treatment.focus) %>%
  summarise_at(vars(Density_per_100_shoots, sqrt.Density_per_100_shoots, gall_survival), funs(mean))
density_means

# plot the distribution of gall density in each treatment
agg_tree.level %>%
  ggplot(., aes(x=Density_per_100_shoots, fill=Treatment.focus)) +
  geom_density(alpha=0.5) +
  geom_vline(data = density_means, aes(xintercept=Density_per_100_shoots, color=Treatment.focus), linetype="dotted")

# plot the distribution of sqrt(gall density) in each treatment
agg_tree.level %>%
  ggplot(., aes(x=sqrt.Density_per_100_shoots, fill=Treatment.focus)) +
  geom_density(alpha=0.5) +
  geom_vline(data = density_means, aes(xintercept=sqrt.Density_per_100_shoots, color=Treatment.focus), linetype="dotted")
```

```{r}
gall_selection.df <- gall_selection.df %>%
  mutate(relative_fitness = ifelse(Treatment.focus=="Control",
                                   gall_survival/filter(size_means, Treatment.focus=="Control")$gall_survival,
                                   gall_survival/filter(size_means, Treatment.focus=="Ectoparasitoid exclusion")$gall_survival))

non_singular <- gall_selection.df %>%
  filter(Plant_Position %in% plants_manygalls) %>%
  group_by(Genotype, Treatment.focus, Plant_Position) %>%
  summarise_at(vars(gall_survival), mean) %>%
  filter(gall_survival > 0 & gall_survival < 1)

size.gradients_plant.level <- gall_selection.df %>%
  filter(Plant_Position %in% non_singular$Plant_Position) %>%
  group_by(Genotype, Treatment.focus, Plant_Position) %>%
  do(model = lm(I(gall_survival/mean(gall_survival)) ~ I(Gall_Height_mm-mean(Gall_Height_mm)), .)) %>%
  tidy(model) %>%
  filter(term != "(Intercept)")

size.gradients_plant.level
summary(lm(estimate ~ Genotype*Treatment.focus, data=size.gradients_plant.level, weights = std.error))
ggplot(size.gradients_plant.level, aes(x=Genotype, y=estimate, fill=Treatment.focus, size=std.error)) +
  geom_point()
```



Understanding the causes of selection in different environments is not straightforward.

The most straightforward way to measure selection is the *selection differential*, which corresponds to the difference in mean phenotype before vs. after selection: $$s=\bar{z}^*-\bar{z}$$.




We find that the selection differential on control trees ($s=$`r round(filter(size_differentials, Treatment.focus=="Control")$selection_differential,2)`) is 43% larger than on treatment trees ($s=$`r round(filter(size_differentials, Treatment.focus=="Ectoparasitoid exclusion")$selection_differential, 2)`). 

We can also look at selection in another way. Let's plot the relationship between absolute fitness and the phenotype.
```{r figure: gall size linear regression, echo=FALSE, message=FALSE, warning=FALSE}
gall_selection.df %>%
  ggplot(., aes(x=Gall_Height_mm - mean(Gall_Height_mm), y=gall_survival, color=Treatment.focus)) +
  geom_smooth(method="lm") +
  geom_jitter(height=0.05, shape=1) +
  geom_hline(data = size_means, aes(yintercept=gall_survival, color=Treatment.focus), linetype="dotted") +
  geom_vline(xintercept=0, color="grey")
```

That's interesting, the slope of absolute fitness as a function of phenotype doesn't look all that different between treatments, but the differences in mean fitness are:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
size_lm <- lm(gall_survival ~ 
                Treatment.focus + 
                I(Gall_Height_mm - mean(Gall_Height_mm)) +  
                Treatment.focus:I(Gall_Height_mm - mean(Gall_Height_mm)), 
              data = gall_selection.df)
summary(size_lm)

size.gradient_lm <- lm(relative_fitness ~ 
                #Treatment.focus + 
                I(Gall_Height_mm - mean(Gall_Height_mm)) +  
                Treatment.focus:I(Gall_Height_mm - mean(Gall_Height_mm)), 
              data = gall_selection.df)
summary(size.gradient_lm)
```

This suggests that the difference in selection between the control and treatment trees is due to differences in fitness between treatments and NOT the relationship between phenotype and fitness. In case you don't believe me, let me convince you that we can recover the selection differentials from a linear model such as this. Note that another way we can define the selection differential is: $$s=\frac{Cov(W,z)}{\bar{W}}$$

where $$W$$ represents absolute fitness and $$z$$ represents the phenotype. In linear model, the regression coefficient $b$ corresponds to: $$b=\frac{Cov(W,z)}{Var(z)}$$

Thus, $$s=b\cdot\frac{Var(z)}{\bar{W}}$$

`r 0.081308*filter(size_means_diffs, Timing=="Before",Treatment.focus=="Control")$Gall_Height_mm_var/filter(size_means_diffs, Timing=="Before",Treatment.focus=="Control")$gall_survival_mean`

```{r figure: gall size logistic regression, echo=FALSE, message=FALSE, warning=FALSE}
binomial_smooth <- function(...) {
  geom_smooth(method = "glm", method.args = list(family = "binomial"), ...)
}

gall_selection.df %>%
  ggplot(., aes(x=Gall_Height_mm - mean(Gall_Height_mm), y=gall_survival, color=Treatment.focus)) +
  binomial_smooth() +
  geom_jitter(height=0.05, shape=1) +
  geom_hline(data = size_means, aes(yintercept=gall_survival, color=Treatment.focus), linetype="dotted") +
  geom_vline(xintercept=0, color="grey")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
indiv_lm <- lm(gall_survival ~ 
                Treatment.focus + 
                I(gall_individuals - mean(gall_individuals)) +  
                Treatment.focus:I(gall_individuals - mean(gall_individuals)), 
              data = agg_gall.level)
summary(indiv_lm)

agg_gall.level <- agg_gall.level %>%
  mutate(relative_fitness = ifelse(Treatment.focus=="Control",
                                   gall_survival/filter(indiv_means, Treatment.focus=="Control")$gall_survival,
                                   gall_survival/filter(indiv_means, Treatment.focus=="Ectoparasitoid exclusion")$gall_survival))

indiv.gradient_lm <- lm(relative_fitness ~ 
                #Treatment.focus + 
                I(gall_individuals - mean(gall_individuals)) +  
                Treatment.focus:I(gall_individuals - mean(gall_individuals)), 
              data = agg_gall.level)
summary(indiv.gradient_lm)
```

```{r figure: gall individuals logistic regression, echo=FALSE, message=FALSE, warning=FALSE}
agg_gall.level %>%
  ggplot(., aes(x=gall_individuals - mean(gall_individuals), y=gall_survival, color=Treatment.focus)) +
  binomial_smooth() +
  geom_jitter(height=0.05, shape=1) +
  #geom_hline(data = size_means, aes(yintercept=gall_survival, color=Treatment.focus), linetype="dotted") +
  geom_vline(xintercept=0, color="grey")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
density_lm <- lm(gall_survival ~ 
                Treatment.focus + 
                I(Density_per_100_shoots - mean(Density_per_100_shoots)) +  
                Treatment.focus:I(Density_per_100_shoots - mean(Density_per_100_shoots)), 
              data = agg_tree.level)
summary(density_lm)

agg_tree.level <- agg_tree.level %>%
  mutate(relative_fitness = ifelse(Treatment.focus=="Control",
                                   gall_survival/filter(density_means, Treatment.focus=="Control")$gall_survival,
                                   gall_survival/filter(density_means, Treatment.focus=="Ectoparasitoid exclusion")$gall_survival))

density.gradient_lm <- lm(relative_fitness ~ 
                #Treatment.focus + 
                I(Density_per_100_shoots - mean(Density_per_100_shoots)) +  
                Treatment.focus:I(Density_per_100_shoots - mean(Density_per_100_shoots)), 
              data = agg_tree.level)
summary(density.gradient_lm)
```

```{r figure: gall individuals logistic regression, echo=FALSE, message=FALSE, warning=FALSE}
agg_tree.level %>%
  ggplot(., aes(x=Density_per_100_shoots - mean(Density_per_100_shoots), y=gall_survival, color=Treatment.focus)) +
  binomial_smooth() +
  geom_jitter(height=0.05, shape=1) +
  #geom_hline(data = size_means, aes(yintercept=gall_survival, color=Treatment.focus), linetype="dotted") +
  geom_vline(xintercept=0, color="grey")
```



Visually, we can estimate the selection differentials
```{r}
library(gsg)

# why are these different?
gall_selection.df %>%
  group_by(Treatment.focus) %>%
  do(moments = moments.differentials(z = .$Gall_Height_mm - mean(.$Gall_Height_mm), W = .$gall_survival, standardized = FALSE)) %>%
  tidy(moments)

control.diff <- moments.differentials(
  z = filter(gall_selection.df, Treatment.focus=="Control")$Gall_Height_mm,
  W = filter(gall_selection.df, Treatment.focus=="Control")$gall_survival, 
  standardized = FALSE
)
control.diff

treatment.diff <- moments.differentials(
  z = filter(gall_selection.df, Treatment.focus=="Ectoparasitoid exclusion")$Gall_Height_mm,
  W = filter(gall_selection.df, Treatment.focus=="Ectoparasitoid exclusion")$gall_survival, 
  standardized = FALSE
)
treatment.diff




```




## Calculating selection differentials

```{r}


size_lms <- gall_selection.df %>%
  group_by(Treatment.focus) %>%
  do(model = lm(gall_survival ~ I(Gall_Height_mm - mean(Gall_Height_mm)), .)) %>%
  tidy(model)
size_lms

summary(lm(gall_survival ~ I(Gall_Height_mm-mean(Gall_Height_mm)), data = filter(gall_selection.df, Treatment.focus=="Control")))

#size_vars <- gall_selection.df %>%
#  group_by(Treatment.focus) %>%
#  summarise_at(vars(Gall_Height_mm), funs(var,sd))
#size_vars

size_lms %>%
  select(Treatment.focus, term, estimate) %>%
  spread(term, estimate) %>%
  mutate(selection_differential = `I(Gall_Height_mm - mean(Gall_Height_mm))`/`(Intercept)`)


gall_selection.df %>%
  do(model = lm(gall_survival ~ I(Gall_Height_mm - mean(Gall_Height_mm))*Treatment.focus, .)) %>%
  tidy(model)

## calculating selection gradients
gall_selection.df <- gall_selection.df %>%
  mutate(relative_fitness = ifelse(Treatment.focus == "Control", 
                                   gall_survival/filter(size_means, Treatment.focus=="Control")$gall_survival,
                                   gall_survival/filter(size_means, Treatment.focus=="Ectoparasitoid exclusion")$gall_survival))

gall_selection.df %>%
  ggplot(., aes(x=Gall_Height_mm - mean(Gall_Height_mm), y=relative_fitness, color=Treatment.focus)) +
  geom_jitter(height=0.02) +
  geom_smooth(method="lm") + 
  geom_hline(yintercept=1, color="grey", linetype="dotted") +
  geom_vline(xintercept=0, color="grey")

size_gradients <- gall_selection.df %>%
  group_by(Treatment.focus) %>%
  do(model = lm(relative_fitness ~ I(Gall_Height_mm - mean(Gall_Height_mm)), .)) %>%
  tidy(model)
size_gradients


summary(lm(relative_fitness ~ I(scale(Gall_Height_mm)), data = filter(gall_selection.df, Treatment.focus=="Control")))

# for standardized selection gradients
gall_selection.df %>%
  group_by(Treatment.focus) %>%
  do(model = lm(relative_fitness ~ I((Gall_Height_mm - mean(Gall_Height_mm))/sd(Gall_Height_mm)), .)) %>%
  tidy(model)

cov12 <- with(filter(gall_selection.df, Treatment.focus=="Ectoparasitoid exclusion"), cov(relative_fitness, Gall_Height_mm))
sd1 <- with(filter(gall_selection.df, Treatment.focus=="Ectoparasitoid exclusion"), sd(Gall_Height_mm))
var1 <- with(filter(gall_selection.df, Treatment.focus=="Ectoparasitoid exclusion"), var(Gall_Height_mm))
sd2 <- with(filter(gall_selection.df, Treatment.focus=="Ectoparasitoid exclusion"), sd(relative_fitness))

cov12/var1
```

Unstandardized b coefficient is equal to Cov(x,y)/var(x).

$$b=\frac{Cov(x,y)}{Var(x)}$$

Standardized cofficient (Beta) is equal to Cov(x,y)/var(x)SD(x)/SD(y)

$$\beta=\frac{Cov(x,y)}{SD(x)SD(x)}\cdot\frac{SD(x)}{SD(y)}$$

$$w=\frac{W}{\hat{W}}$$

$$s=Cov(w,z)$$
also

$$s=\frac{Cov(W,z)}{\hat{W}}$$

Selection differentials can be calculated as the covariance between the phenotype and absolute fitness, cov(W,z), divided by mean fitness. If we additionally standardize the scale of the phenotype by dividing by its variance, then we also get the selection gradient.


Calculate the selection differentials (difference in means) before and after selection for each treatment.
```{r}
size_means <- gall_diffs.df %>%
  group_by(Timing, Treatment.focus) %>%
  summarise_at(vars(Gall_Height_mm), funs(mean)) %>%
  ungroup() 
size_means

size_diffs <- size_means %>%
  spread(Timing, Gall_Height_mm) %>%
  mutate(selection_differential = After - Before)
size_diffs

gall_diffs.df %>%
  ggplot(., aes(x=Gall_Height_mm, fill=Timing)) +
  geom_density(alpha=0.5) +
  geom_vline(data = size_means, aes(xintercept=Gall_Height_mm, color=Timing), linetype="dotted") +
  facet_wrap(~Treatment.focus, ncol=1)
```

Calculate selection differentials for scaled and normalized traits
```{r}
sc.sqrt.size_means <- gall_diffs.df %>%
  group_by(Timing, Treatment.focus) %>%
  summarise_at(vars(sc.sqrt.Gall_Height_mm), funs(mean)) %>%
  ungroup() 
sc.sqrt.size_means

sc.sqrt.size_diffs <- sc.sqrt.size_means %>%
  spread(Timing, sc.sqrt.Gall_Height_mm) %>%
  mutate(selection_differential = After - Before)
sc.sqrt.size_diffs

gall_diffs.df %>%
  ggplot(., aes(x=sc.sqrt.Gall_Height_mm, fill=Timing)) +
  geom_density(alpha=0.5) +
  geom_vline(data = sc.sqrt.size_means, aes(xintercept=sc.sqrt.Gall_Height_mm, color=Timing), linetype="dotted") +
  facet_wrap(~Treatment.focus, ncol=1)
```

```{r}

gall_selection.df %>%
  group_by(Treatment.focus) %>%
  summarise(covariance = cov(gall_survival, Gall_Height_mm),
            mean_fitness = mean(gall_survival)) %>%
  mutate(selection_differential = covariance/mean_fitness)

gall_selection.df %>%
  group_by(Treatment.focus) %>%
  summarise(covariance = cov(gall_survival, sc.sqrt.Gall_Height_mm),
            mean_fitness = mean(gall_survival)) %>%
  mutate(selection_differential = covariance/mean_fitness)

summary(lm(gall_survival ~ sc.sqrt.Gall_Height_mm, filter(gall_selection.df, Treatment.focus=="Control")))
summary(lm(gall_survival ~ sc.sqrt.Gall_Height_mm, filter(gall_selection.df, Treatment.focus=="Ectoparasitoid exclusion")))

summary(lm(relative_fitness ~ sc.sqrt.Gall_Height_mm, data=filter(size.rel_fitness.df, Treatment.focus=="Control")))
```

NOTE THAT THE SELECTION DIFFERENTIAL SHOULD CORRESPOND TO THE SELECTION GRADIENT?? (ACCORDING TO HUNTER ET AL 2018, EQN. 4)

Calculate selection gradients acting on gall size
```{r}
size.rel_fitness.df <- gall_selection.df %>%
  mutate(relative_fitness = ifelse(Treatment.focus == "Control", gall_survival/control.mean_fitness, gall_survival/treatment.mean_fitness))

size.rel_fitness.df %>%
  ggplot(., aes(x = Gall_Height_mm, y = relative_fitness, color=Treatment.focus)) +
  geom_jitter(shape=1, height = 0.02) +
  geom_hline(yintercept=1, linetype="dotted") +
  geom_smooth(method = "lm")

size.rel_fitness.df %>%
  ggplot(., aes(x = sc.sqrt.Gall_Height_mm, y = relative_fitness, color=Treatment.focus)) +
  geom_jitter(shape=1, height = 0.02) +
  geom_hline(yintercept=1, linetype="dotted") +
  geom_smooth(method = "lm")

size.rel_fitness.lm <- lm(relative_fitness ~ Gall_Height_mm + Gall_Height_mm:Treatment.focus, data=size.rel_fitness.df)
summary(size.rel_fitness.lm)

sc.sqrt.size.rel_fitness.lm <- lm(relative_fitness ~ sc.sqrt.Gall_Height_mm + sc.sqrt.Gall_Height_mm:Treatment.focus, data=size.rel_fitness.df)
summary(sc.sqrt.size.rel_fitness.lm) 
```

NEED TO CALCULATE SELECTION DIFFERENTIALS AT THE FINEST LEVEL, SINCE THAT IS WHERE SURVIVAL IS ZERO OR 1.

Calculate selection differentials for number of individuals per galls
```{r}
agg_gall.level <- gall_selection.df %>%
  group_by(Treatment.focus, Genotype, Plant_Position, Gall_Number) %>%
  summarise_at(vars(gall_survival, gall_individuals, Gall_Height_mm, Density_per_100_shoots), funs(mean)) %>%
  mutate(sc.log.gall_individuals = as.numeric(scale(log(gall_individuals))))

agg_gall.diffs <- bind_rows(
  mutate(agg_gall.level, Timing = "Before"),
  mutate(filter(agg_gall.level, gall_survival == 1), Timing = "After")
)

indiv_means <- agg_gall.diffs %>%
  group_by(Timing, Treatment.focus) %>%
  summarise_at(vars(gall_individuals, sc.log.gall_individuals), mean, na.rm = TRUE) %>%
  ungroup() 
indiv_means

indiv_diffs <- indiv_means %>%
  select(Timing, Treatment.focus, gall_individuals) %>%
  spread(Timing, gall_individuals) %>%
  mutate(selection_differential = After - Before)
indiv_diffs

sc.log.indiv_diffs <- indiv_means %>%
  select(Timing, Treatment.focus, sc.log.gall_individuals) %>%
  spread(Timing, sc.log.gall_individuals) %>%
  mutate(selection_differential = After - Before)
sc.log.indiv_diffs

agg_gall.diffs %>%
  ggplot(., aes(x=gall_individuals, fill=Timing)) +
  geom_density(alpha=0.5) +
  geom_vline(data = indiv_means, aes(xintercept=gall_individuals, color=Timing), linetype="dotted") +
  facet_wrap(~Treatment.focus, ncol=1)

agg_gall.diffs %>%
  ggplot(., aes(x=sc.log.gall_individuals, fill=Timing)) +
  geom_density(alpha=0.5) +
  geom_vline(data = indiv_means, aes(xintercept=sc.log.gall_individuals, color=Timing), linetype="dotted") +
  facet_wrap(~Treatment.focus, ncol=1)
```


Calculate selection gradients acting on number of individuals per gall
```{r}
agg_gall.control.mean_fit <- mean(filter(agg_gall.level, Treatment.focus=="Control")$gall_survival)
agg_gall.treatment.mean_fit <- mean(filter(agg_gall.level, Treatment.focus=="Ectoparasitoid exclusion")$gall_survival)

agg_gall.level <- agg_gall.level %>%
  mutate(relative_fitness = ifelse(Treatment.focus == "Control", 
                                   gall_survival/agg_gall.control.mean_fit,
                                   gall_survival/agg_gall.treatment.mean_fit))

agg_gall.level %>%
  ggplot(., aes(x = gall_individuals, y = relative_fitness, color=Treatment.focus)) +
  geom_jitter(shape=1, height = 0.02) +
  geom_hline(yintercept=1, linetype="dotted") +
  geom_smooth(method = "lm")

agg_gall.level %>%
  ggplot(., aes(x = sc.log.gall_individuals, y = relative_fitness, color=Treatment.focus)) +
  geom_jitter(shape=1, height = 0.02) +
  geom_hline(yintercept=1, linetype="dotted") +
  geom_smooth(method = "lm")

indiv.gradient.lm <- lm(relative_fitness ~ gall_individuals + gall_individuals:Treatment.focus, agg_gall.level)
summary(indiv.gradient.lm)

sc.log.indiv.gradient.lm <- lm(relative_fitness ~ sc.log.gall_individuals + sc.log.gall_individuals:Treatment.focus, agg_gall.level)
summary(sc.log.indiv.gradient.lm)
```

Calculate selection differentials for gall density
```{r}
agg_tree.level <- gall_selection.df %>%
  group_by(Treatment.focus, Genotype, Plant_Position) %>%
  summarise_at(vars(gall_survival, gall_individuals, Gall_Height_mm, Density_per_100_shoots), funs(mean)) %>%
  mutate(sc.sqrt.Density_per_100_shoots = as.numeric(scale(sqrt(Density_per_100_shoots))))

agg_tree.diffs <- bind_rows(
  mutate(agg_tree.level, Timing = "Before"),
  mutate(filter(agg_tree.level, gall_survival == 1), Timing = "After")
)

density_means <- gall_diffs.df %>%
  distinct(Plant_Position, Timing, Treatment.focus, Density_per_100_shoots) %>%
  group_by(Timing, Treatment.focus) %>%
  summarise_at(vars(Density_per_100_shoots), funs(mean)) %>%
  ungroup() 
density_means

density_diffs <- density_means %>%
  spread(Timing, Density_per_100_shoots) %>%
  mutate(selection_differential = After - Before)
density_diffs

gall_diffs.df %>%
  distinct(Plant_Position, Timing, Treatment.focus, Density_per_100_shoots) %>%
  ggplot(., aes(x=Density_per_100_shoots, fill=Timing)) +
  geom_density(alpha=0.5) +
  geom_vline(data = density_means, aes(xintercept=Density_per_100_shoots, color=Timing), linetype="dotted") +
  facet_wrap(~Treatment.focus, ncol=1)
```

Calculate selection gradients acting on gall density
```{r}
agg_tree.level <- gall_selection.df %>%
  group_by(Treatment.focus, Genotype, Plant_Position) %>%
  summarise_at(vars(gall_survival, gall_individuals, Gall_Height_mm, Density_per_100_shoots), funs(mean)) %>%
  mutate(sc.sqrt.Density_per_100_shoots = as.numeric(scale(sqrt(Density_per_100_shoots)))) 

agg_tree.control.mean_fit <- mean(filter(agg_tree.level, Treatment.focus=="Control")$gall_survival)
agg_tree.treatment.mean_fit <- mean(filter(agg_tree.level, Treatment.focus=="Ectoparasitoid exclusion")$gall_survival)

agg_tree.level <- agg_tree.level %>% 
  mutate(relative_fitness = ifelse(Treatment.focus=="Control", 
                                   gall_survival/agg_tree.control.mean_fit, 
                                   gall_survival/agg_tree.treatment.mean_fit))

agg_tree.level %>%
  ggplot(., aes(x = Density_per_100_shoots, y = relative_fitness, color=Treatment.focus)) +
  geom_jitter(shape=1, height = 0.02) +
  geom_hline(yintercept=1, linetype="dotted") +
  geom_smooth(method = "lm")

agg_tree.level %>%
  ggplot(., aes(x = sc.sqrt.Density_per_100_shoots, y = relative_fitness, color=Treatment.focus)) +
  geom_jitter(shape=1, height = 0.02) +
  geom_hline(yintercept=1, linetype="dotted") +
  geom_smooth(method = "lm")

density.gradient.lm <- lm(relative_fitness ~ Density_per_100_shoots + Density_per_100_shoots:Treatment.focus, agg_tree.level)
summary(density.gradient.lm)

sc.sqrt.density.gradient.lm <- lm(relative_fitness ~ sc.sqrt.Density_per_100_shoots + sc.sqrt.Density_per_100_shoots:Treatment.focus, agg_tree.level)
summary(sc.sqrt.density.gradient.lm)
plot(sc.sqrt.density.gradient.lm) # not too bad
```